Resolving gut microbiome networks within Chiropterans

### 2025-07-07 phasegenome_out/doc/paper/draft_manuscript.rmd
update

@@

```{r Fig6, echo = FALSE, message=FALSE, fig.cap='**Figure 6. Phage-host network analysis.**'}

knitr::include_graphics("../../data/results/figures/phage-host_bat_network_final_04232025.pdf")
```

>>>>

F

@@

# ```{r Fig6, echo = FALSE, message=FALSE, fig.cap='**Figure 6. Phage-host network analysis.**'}
# 
# knitr::include_graphics("../../data/results/figures/phage-host_bat_network_final_04232025.pdf")
# ```
